---
title: "results"
output: html_notebook
---
```{r include=FALSE}
set.seed(1)
library(brms) 
library(patchwork)
library(tidyverse)
library(tidybayes)
library(bayesplot)
library(RColorBrewer)
library(knitr) 
library(kableExtra)
library(scales)
library(scatterpie)
library(here)
knitr::opts_chunk$set(fig.path='figures/')
blues <- brewer.pal(9, "Blues")[3:9] 
greens <- brewer.pal(9, "Greens")[3:9] 
oranges <- brewer.pal(9, "Oranges")[3:9] 
clrs <- RColorBrewer::brewer.pal(8, "Set1")

custom_theme <- theme_bw() +
  theme(
    text = element_text(size = 20), 
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(), 
   # legend.position = "none", 
#    axis.title.x = element_blank(),
#    axis.title.y = element_blank(),
    panel.border = element_blank(),             # Remove all borders
    axis.line.x = element_line(color = "black", size = 0.5),  # Add bottom border
    axis.line.y = element_line(color = "black", size = 0.5),  # Add left border
  )

# Apply the custom theme globally
theme_set(custom_theme)
```
# Study 1
```{r}
m_1_plus <- readRDS("saves/study1/s1-age-domain_ID_age-domain_Sce_age-domain.rds")
m_1_interaction <- readRDS("saves/study1/s1-age-x-domain_ID_age-domain_Sce_age-domain.rds")
m_1_cap_null <- readRDS("saves/study1/s1-age_ID_age_Sce_age.rds")

loo_compare(m1_interaction, m_1_cap_null)
loo_compare(m_1_plus, m_1_cap_null)  # capacity vs. no capacity 
loo_compare(m_1_plus, m1_interaction)  # capacity as interaction vs. as main

m_1 <- m_1_interaction
print(m_1$formula)

pred_m1 <- predict(m_1) %>%
  as_tibble() %>%
  bind_cols(m_1$data)

newdata <- distinct(m_1$data, age_factor, domain) 
fitted_m1 <- fitted(m_1, re_formula = NA, newdata=newdata)%>%
  as_tibble() %>%
  bind_cols(newdata)

post_draws_m1<- posterior_predict(m_1, draws = 200) %>%
  as_tibble()
```
### general average
People are estimated more likely to commit wrongdoing as the story describes estimate that at younger ages.
```{r}
df <- m_1$data
p1 <- fitted_m1 %>% 
  ggplot(aes(x = age_factor, y = Estimate, group=domain)) +
  geom_point(data=df, aes(x = age_factor, y=r1, color=domain), alpha=0.2, size=1, position=position_dodge(width=0.4)) +
  geom_line(aes(color=domain), size=2, alpha=0.8) + 
  scale_color_brewer(palette = "Set1", labels = c("Motor control", "Inhibitory control", "Planning", "ToM", "Moral competence"), name = "Control type") +
  ylab("Expectation") + xlab("Age") +
  scale_y_continuous(limits = c(0, 1), breaks = c(seq(0, 1, 0.2)), labels = c(seq(0, 100, 20))) +
  theme_bw() +
  theme(text = element_text(size = 20), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  guides(fill = guide_legend(title = NULL))

ggsave("saves/figures/r1.pdf", width = 8, height = 5)
p1
```
### domain average
```{r}
age_levels_s1 <- unique(m_1$data$age_factor)
domain_levels <- unique(m_1$data$domain)

# >
hypothesis_results_age2 <- hypothesis(m_1, c("domaininhibit = domaintom", # + Intercepts on both sides
                    "domaininhibit = domainplan",
                    "domaininhibit = 0", # compare to Intercept (age 2 domain motor)
                    "domaininhibit = domainmoral", 
                    "domaintom = 0",  
                    "domaintom = domainplan",
                    "domaintom = domainmoral",
                    "domainplan = 0",
                    "domainplan = domainmoral",
                    "domainmoral = 0"
                    ))

hypothesis_results <- list()
for (age in age_levels_s1[2:11]) {
  hypothesis_expressions <- c(
    paste0("age_factor", age, ":domaininhibit + domaininhibit = age_factor", age, ":domaintom + domaintom"),
    paste0("age_factor", age, ":domaininhibit + domaininhibit = age_factor", age, ":domainplan + domainplan"),
    paste0("age_factor", age, ":domaininhibit + domaininhibit = 0"),
    paste0("age_factor", age, ":domaininhibit + domaininhibit = age_factor", age, ":domainmoral + domainmoral"),
    paste0("age_factor", age, ":domaintom + domaintom = 0"),
    paste0("age_factor", age, ":domaintom + domaintom = age_factor", age, ":domainplan + domainplan"),
    paste0("age_factor", age, ":domaintom + domaintom = age_factor", age, ":domainmoral + domainmoral"),
    paste0("age_factor", age, ":domainplan + domainplan = 0"),
    paste0("age_factor", age, ":domainplan + domainplan = age_factor", age, ":domainmoral + domainmoral"),
    paste0("age_factor", age, ":domainmoral + domainmoral = 0")
  )
  hypothesis_result <- hypothesis(m_1, hypothesis_expressions)
  hypothesis_results[[paste0("age", age)]] <- hypothesis_result
}

create_hypothesis_domain_age <- function(age_levels, domain_levels, sign){
  # non-base-level domains
  hyp = c()
  for (d in array(domain_levels[2:5])){
    hyp = c(hyp, paste0("domain", d, sign, "age_factor", age_levels[2], ":domain", d, "+ age_factor", age_levels[2])) # age 2
    for (i in 2:(length(age_levels) - 1)) {
      age_start <- age_levels[i] 
      age_end <- age_levels[i + 1]
      hyp = c(hyp, paste0("age_factor",age_start, ":domain", d, "+ age_factor", age_start, sign, " age_factor",age_end, ":domain", d, "+ age_factor", age_end))
    }
  }
  # base-level domain
  hyp = c(hyp, paste0("0", sign, "age_factor", age_levels[2])) # age 2
  for (i in 2:(length(age_levels) - 1)) {
      age_start <- age_levels[i] 
      age_end <- age_levels[i + 1]
      hyp = c(hyp, paste0("age_factor", age_start, sign, "age_factor", age_end))
  }
  
  return(hyp)
}

print_table <- function(hypothesis_results){
  tab = hypothesis_results$hypothesis %>% 
    mutate(across(where(is.numeric), ~comma(., accuracy=0.01))) %>% 
    rename_all(~gsub("\\.", " ", .))
  a = map_chr(tab, ~ifelse(class(.x)=="numeric", "r","l"))
  tab %>% 
    kbl(caption= "Model results with kable", align=a) %>% 
    kable_styling(full_width=FALSE, 
                  bootstrap_options = c("striped", "hover", "condensed"))
}

hyp <- create_hypothesis_domain_age(age_levels_s1, domain_levels, ">")
hypothesis_results_ages <- hypothesis(m_1, hyp)
print_table(hypothesis_results_ages)

teen_adult_hypothesis <- hypothesis(m_1, c('age_factor16 > age_factor30', 'age_factor16:domaininhibit+ age_factor16> age_factor30:domaininhibit+ age_factor30', 'age_factor16:domainplan+ age_factor16> age_factor30:domainplan+ age_factor30', 'age_factor16:domaintom+ age_factor16> age_factor30:domaintom+ age_factor30', 'age_factor16:domainmoral+ age_factor16> age_factor30:domainmoral+ age_factor30'))

print_table(teen_adult_hypothesis)

```

### variation
The beliefs are most diverse for the youngest age, and monotonically decreases over the character’s age. 
```{r}
df <- m_1$data
df %>%
  group_by(age_factor) %>%
  summarise(std = sd(r1))
```
### compare growth statistics 
Which age grows fastest 
```{r}
calculate_stat_change_rates <- function(samples, model){
  df <- model$data
  age_levels <- unique(df$age_factor)
  domain_levels <- unique(df$domain)
  
  calculate_change_rates <- function(posterior_samples, age_levels, domain) {
    change_rates <- data.frame()
    for (i in 1:(length(age_levels) - 1)) {
      age_start <- age_levels[i] 
      age_end <- age_levels[i + 1]
      if (age_start != "2" && domain !="motor"){
      change_rate <- ( posterior_samples[[paste0("b_age_factor", age_end)]] 
                       + posterior_samples[[paste0("b_age_factor", age_end, ":domain", domain)]] 
                       - posterior_samples[[paste0("b_age_factor", age_start)]]
                       - posterior_samples[[paste0("b_age_factor", age_start, ":domain", domain)]]
                     ) 
      }
      else if (age_start == "2" && domain!="motor"){
        change_rate <- posterior_samples[["b_age_factor4"]] + posterior_samples[[paste0("b_age_factor4:domain", domain)]] 
      }
      else if (age_start == "2" && domain=="motor"){
        change_rate <- posterior_samples[["b_age_factor4"]] 
      }
     else if (age_start != "2" && domain=="motor"){
        change_rate <- posterior_samples[[paste0("b_age_factor", age_end)]] - posterior_samples[[paste0("b_age_factor", age_start)]]
      }
     else { print(".")}
      
     change_rates <- rbind(change_rates, data.frame(sample = 1:nrow(posterior_samples), age_start = age_start, age_end = age_end, change_rate = change_rate))
    }
    return(change_rates)
  }
  
  domain_change_rates <- lapply(domain_levels, function(domain) {
    calculate_change_rates(samples, age_levels, domain)
  })
  names(domain_change_rates) <- domain_levels
  
  stat_change_rates <- map_dfr(domain_levels, function(domain) {
    domain_change_rates[[domain]] %>%
      group_by(sample) %>%
      summarise(avg_change_rate = mean(change_rate), 
                var_change_rate = var(change_rate, na.rm = TRUE),
                range_change_rate = max(change_rate) - min(change_rate),
                whichmax = which.max(change_rate),
                max_abs_growth = max(change_rate),
                age_max_growth = as.numeric(age_start[which.max(abs(change_rate))]),
                check_age_growth= change_rate[age_start==age_start[which.max(abs(change_rate))]]) %>%
      mutate(domain = domain)
  })
 
  return(stat_change_rates)
}

plot_age_max_change <- function(stat_change_rates, age_levels){
  p <- ggplot(stat_change_rates, aes(x = age_max_growth, fill = domain)) +
    geom_bar(position = "dodge") +
    scale_fill_brewer(palette = "Set1") +
    scale_x_discrete(labels = age_levels) +
    labs(#title = "Distributions of Age of Max Growth",
         x = "Age of Maximal Change",
         y = "Count",
         fill = "Domain") +
    theme_bw() +
    theme(text = element_text(size = 20), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    facet_wrap(~domain, ncol = 1) + 
    guides(color = guide_legend(title = NULL))
  
  return(p)
}

posterior_samples_m1 <- as_draws_df(m_1)
stat_change_rates_m1 <- calculate_stat_change_rates(posterior_samples_m1, m_1)

plot_age_max_change(stat_change_rates_m1, age_levels_s1) 
ggsave("figures/m1-age-max-growth.pdf", width = 10, height = 6)

```

### combined figure
```{r}
age_levels_s1 <- unique(m_1$data$age_factor)
domain_levels <- unique(m_1$data$domain)

newdata <- distinct(m_1$data, age_factor, domain) 
fitted_m1 <- fitted(m_1, re_formula = NA, newdata=newdata)%>%
  as_tibble() %>%
  bind_cols(newdata)

df <- m_1$data

posterior_samples_m1 <- as_draws_df(m_1)
stat_change_rates_m1 <- calculate_stat_change_rates(posterior_samples_m1, m_1)

stat_change_rates_m1 <- stat_change_rates_m1 %>%
    group_by(domain, age_max_growth) %>%
    summarise(count = n()) %>%
    mutate(proportion = count / sum(count))
  
p1 <- fitted_m1 %>% 
  ggplot(aes(x = age_factor, y = Estimate, group=domain)) +
  geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5, group=domain, fill=domain), alpha=0.1) + 
  geom_point(data=df, aes(x = age_factor, y=r1, color=domain), alpha=0.2, size=1, position=position_dodge(width=0.4)) +
  geom_line(aes(color=domain), size=2, alpha=0.8) + 
  scale_color_brewer(palette = "Set1", labels = c("Motor control", "Inhibitory control", "Planning", "ToM", "Moral competence"), name = "") +
  scale_fill_brewer(palette = "Set1", labels = c("Motor control", "Inhibitory control", "Planning", "ToM", "Moral competence"), guide = "none") +  
  ylab("Expected likelihood") + xlab("Age") +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2), labels = scales::percent) +
  guides(fill = "none", color = guide_legend(title = NULL))  # Explicitly remove fill guide

p2 <- ggplot(stat_change_rates_m1, aes(x = age_levels_s1[age_max_growth], y=proportion, fill = domain, color=domain)) +
    geom_bar(position = "dodge", stat = "identity", alpha=0.6) +
    scale_fill_brewer(palette = "Set1", labels = c("Motor control", "Inhibitory control", "Planning", "ToM", "Moral competence"), guide='none') +  
    scale_color_brewer(palette = "Set1", labels = c("Motor control", "Inhibitory control", "Planning", "ToM", "Moral competence"), name="", guide='none') +
    scale_x_discrete(labels = age_levels_s1) +
    scale_y_continuous(breaks = seq(0, 1, 0.2), labels = scales::percent) + 
    labs(x = "Age of maximal change", y = "% posterior draws") +
    facet_wrap(~domain, ncol = 1) + 
    theme(
      strip.background = element_blank(),
      strip.text.x = element_blank(),
      legend.position = "none"  # This ensures no legend appears
    )

combined_plot <- p1 + p2 + plot_layout(guides = "collect", widths=c(2,1)) & 
  theme(legend.position = 'bottom')  # Only color legend should be collected

print(combined_plot)

ggsave("figures/m1-combine.pdf", width = 12, height = 6)
```
# Study 2
### Information criteria
```{r}
m_2_interaction <- readRDS(here("saves/study2/s2-age-x-domain_ID_age-domain_Sce_age-domain.rds"))
print(m_2$formula)
m_2_null <- readRDS("saves/study2/s2-age_ID_age_Sce_age.rds")
print(m_2_null$formula)
m_2_plus <- readRDS("saves/study2/s2-age-domain_ID_age-domain_Sce_age-domain.rds")
df_2 <- m_2$data

loo_compare(m_2, m_2_interaction)

m_2 <- m_2_plus
m_2 <- m_2_interaction  # for comparison with study 1 use this model to make figure
```
### domain average, significant differences
```{r}
hyp <- create_hypothesis_domain_age(age_levels_s1, domain_levels, "<")
hypothesis(m_2, hyp)
```
### combined figure
```{r}
newdata <- distinct(m2_plus$data, age_factor, domain)
fitted_m2 <- fitted(m2_plus, re_formula = NA, newdata=newdata)%>%
  as_tibble() %>%
  bind_cols(newdata)

posterior_samples_m2 <- as_draws_df(m2_plus)
stat_change_rates_m2 <- calculate_stat_change_rates(posterior_samples_m2, m_2)

stat_change_rates_m2 <- stat_change_rates_m2 %>%
    group_by(domain, age_max_growth) %>%
    summarise(count = n()) %>%
    mutate(proportion = count / sum(count))

df_2 <- m_2$data
p1 <- fitted_m2 %>% 
  ggplot(aes(x = age_factor, y = Estimate, group=domain)) +
  geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5, group=domain, fill=domain), alpha=0.1) + 
  geom_point(data=df_2, aes(x = age_factor, y=r2, color=domain), alpha=0.2, size=1, position=position_dodge(width=0.4)) +
  geom_line(aes(color=domain), size=2, alpha=0.8) + 
  scale_color_brewer(palette = "Set1", labels = c("Motor control", "Inhibitory control", "Planning", "ToM", "Moral competence"), name = "") +
  scale_fill_brewer(palette = "Set1", labels = c("Motor control", "Inhibitory control", "Planning", "ToM", "Moral competence"), guide = "none") +
  ylab("Responsibility") + xlab("Age") +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2), labels = scales::percent)

p2 <- ggplot(stat_change_rates_m2, aes(x = age_levels_s1[age_max_growth], y=proportion, color = domain, fill=domain)) +
    geom_bar(position = "dodge", stat = "identity", alpha=0.6) +
    scale_color_brewer(palette = "Set1", labels = c("Motor control", "Inhibitory control", "Planning", "ToM", "Moral competence"), name = "Control type", guide='none') +
    scale_fill_brewer(palette = "Set1", labels = c("Motor control", "Inhibitory control", "Planning", "ToM", "Moral competence"), name = "Control type", guide = 'none') +
    scale_x_discrete(labels = age_levels_s1) +
    scale_y_continuous(breaks = seq(0, 1, 0.2), labels = scales::percent) + 
    labs(x = "Age of Maximal Change",
         y = "% posterior draws",
         fill = "Control type") +
    # run customized theme in beginning instead
    facet_wrap(~domain, ncol = 1) + 
    theme(
      strip.background = element_blank(),
      strip.text.x = element_blank(),
      legend.position = "right"
    )

combined_plot <- p1 + p2 + plot_layout(guides = "collect", widths=c(2,1)) & theme(legend.position = 'bottom') 
print(combined_plot)

ggsave("figures/m2-combine.pdf", width = 12, height = 6)
```
### variation
```{r}
df <- m_2$data
df %>%
  group_by(age_factor) %>%
  summarise(std = sd(r2))
```

# Study 3
```{r}
m_3 <- readRDS("saves/study3/s3-age-x-r1_ID_age-r1_Domain_age-x-r1_Sce_age-r1.rds")

m3r1 <- readRDS("saves/study3/s3-r1-separate-age-x-domain_ID_age-domain_Sce_age-domain.rds")
m3r2 <- readRDS("saves/study3/s3-r2-separate-age-x-domain_ID_age-domain_Sce_age-domain.rds")

age_levels_s3 <- unique(m_3$data$age_factor)
domain_levels <- unique(m_3$data$domain)

df <- m_3$data %>%
  mutate(r1 = (r1_scale * attr(m_3$data$r1_scale, "scaled:scale") + attr(m_3$data$r1_scale, "scaled:center") ) )

post_m3 <- predict(m_3) %>%
  as_tibble() %>%
  bind_cols(m_3$data) 

newdata <- crossing(distinct(m3r1$data, age_factor, domain))
fitted_m3r1 <- fitted(m3r1, re_formula = NA, newdata=newdata) %>% as_tibble() %>% bind_cols(newdata)

newdata <- crossing(distinct(m3r2$data, age_factor, domain))
fitted_m3r2 <- fitted(m3r2, re_formula = NA, newdata=newdata) %>% as_tibble() %>% bind_cols(newdata)

newdata <- crossing(r1_scale = c(-1, 0, 1), age_factor = age_levels_s3)
fitted_m3r1r2 <- fitted(m_3, re_formula = NA, newdata=newdata)%>% as_tibble() %>% bind_cols(newdata)
```

### plot figure
```{r}
p0 <- fitted_m3r1r2 %>%
  ggplot(aes(x = age_factor, y = Estimate)) +
  # geom_point(aes(y=Estimate, color=factor(r1_scale)),size=2, position=position_dodge(width=0.6)) +
  geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5, group=r1_scale, fill=factor(r1_scale)), alpha=0.1) + 
  geom_path(aes(group=r1_scale, color= factor(r1_scale)), size=2) +
  scale_fill_manual(values = c(blues[3], blues[5], blues[7]), guide = "none") +
  scale_colour_manual(values = c(blues[3], blues[5], blues[7]), labels=c("Lower likelihood", "Average", "Higher likelihood"), name = "") +
  ylab("Responsibility") + xlab("Age") +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2), labels = scales::percent)

p1 <- fitted_m3r1 %>% 
  ggplot(aes(x = age_factor, y = Estimate, group=domain)) +
  geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5, group=domain, fill=domain), alpha=0.1) + 
  #geom_point(data= m3r1$data, aes(x = age_factor, y=r1_01, color=domain), alpha=0.1, size=0.5, position=position_dodge(width=0.4)) +
  geom_line(aes(color=domain), size=1, alpha=0.8) + 
  scale_color_brewer(palette = "Set1", labels = c("Motor control", "Inhibitory control", "Planning", "ToM", "Moral competence"), name = "") +
  scale_fill_brewer(palette = "Set1", labels = c("Motor control", "Inhibitory control", "Planning", "ToM", "Moral competence"), guide = "none") +  
  ylab("Expected likelihood") + xlab("Age") +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2), labels = scales::percent) +
  guides(fill = "none", color = guide_legend(nrow = 3,title = NULL)) +
  theme(text = element_text(size = 15))

p2 <- fitted_m3r2 %>% 
  ggplot(aes(x = age_factor, y = Estimate, group=domain)) +
  geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5, group=domain, fill=domain), alpha=0.1) + 
  #geom_point(data= m3r2$data, aes(x = age_factor, y=r2, color=domain), alpha=0.1, size=0.5, position=position_dodge(width=0.4)) +
  geom_line(aes(color=domain), size=1, alpha=0.8) + 
  scale_color_brewer(palette = "Set1", labels = c("Motor control", "Inhibitory control", "Planning", "ToM", "Moral competence"), name = "") +
  scale_fill_brewer(palette = "Set1", labels = c("Motor control", "Inhibitory control", "Planning", "ToM", "Moral competence"), guide = "none") +
  ylab("Responsibility") + xlab("Age") +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2), labels = scales::percent) +
  guides(fill = "none", color = guide_legend(nrow = 3, title = NULL)) +
  theme(text = element_text(size = 15))


r3fig <- p0 + (p1 / p2) + plot_layout(widths=c(2,1), guides = "collect") & theme(legend.position = 'bottom') 

print(r3fig)

ggsave("figures/m3-combine.pdf", r3fig, width = 12, height = 6)

```

### replicate distribution of age of maximal change
```{r}
# age category differ from s1 and s2
calculate_stat_change_rates_s3 <- function(samples, model){
  df <- model$data
  age_levels <- unique(df$age_factor)
  domain_levels <- unique(df$domain)
  
  calculate_change_rates <- function(posterior_samples, age_levels, domain) {
    change_rates <- data.frame()
    for (i in 1:(length(age_levels) - 1)) {
      age_start <- age_levels[i] 
      age_end <- age_levels[i + 1]
      if (age_start != "2" && domain !="motor"){
      change_rate <- ( posterior_samples[[paste0("b_age_factor", age_end)]] 
                       + posterior_samples[[paste0("b_age_factor", age_end, ":domain", domain)]] 
                       - posterior_samples[[paste0("b_age_factor", age_start)]]
                       - posterior_samples[[paste0("b_age_factor", age_start, ":domain", domain)]]
                     ) 
      }
      else if (age_start == "2" && domain!="motor"){
        change_rate <- posterior_samples[["b_age_factor5"]] + posterior_samples[[paste0("b_age_factor5:domain", domain)]] 
      }
      else if (age_start == "2" && domain=="motor"){
        change_rate <- posterior_samples[["b_age_factor5"]] 
      }
     else if (age_start != "2" && domain=="motor"){
        change_rate <- posterior_samples[[paste0("b_age_factor", age_end)]] - posterior_samples[[paste0("b_age_factor", age_start)]]
      }
     else { print("there is NA")
      }
      
     change_rates <- rbind(change_rates, data.frame(sample = 1:nrow(posterior_samples), age_start = age_start, age_end = age_end, change_rate = change_rate))
    }
    return(change_rates)
  }
  
  domain_change_rates <- lapply(domain_levels, function(domain) {
    calculate_change_rates(samples, age_levels, domain)
  })
  names(domain_change_rates) <- domain_levels
  
  stat_change_rates <- map_dfr(domain_levels, function(domain) {
    domain_change_rates[[domain]] %>%
      group_by(sample) %>%
      summarise(avg_change_rate = mean(change_rate), 
                var_change_rate = var(change_rate, na.rm = TRUE),
                range_change_rate = max(change_rate) - min(change_rate),
                whichmax = which.max(change_rate),
                max_abs_growth = max(change_rate),
                age_max_growth = as.numeric(age_start[which.max(abs(change_rate))]),
                check_age_growth= change_rate[age_start==age_start[which.max(abs(change_rate))]]) %>%
      mutate(domain = domain)
  })
 
  return(stat_change_rates)
}

posterior_samples_m3r1 <- as_draws_df(m3r1)
stat_change_rates_m3r1 <- calculate_stat_change_rates_s3(posterior_samples_m3r1, m3r1)
plot_age_max_change(stat_change_rates_m3r1, age_levels_s3) 

ggsave("figures/m3r1-age-max-growth.pdf", width = 10, height = 6)

posterior_samples_m3r2 <- as_draws_df(m3r2)
stat_change_rates_m3r2 <- calculate_stat_change_rates_s3(posterior_samples_m3r2, m3r2)
plot_age_max_change(stat_change_rates_m3r2, age_levels_s3)
ggsave("figures/m3r2-age-max-growth.pdf", width = 10, height = 6)
```

## domain average, significant differences
```{r}
age_levels_s3 <- unique(m3r1$data$age_factor)

hyp_m3r1 <- create_hypothesis_domain_age(age_levels_s3, domain_levels, ">")
hypothesis_results <- hypothesis(m3r1, hyp_m3r1)
print(hypothesis_results$hypothesis)
write.csv(hypothesis_results$hypothesis, "saves/study3/s3r1-hypothesis-contrast-domain.csv", row.names = FALSE)

hyp_m3r2 <- create_hypothesis_domain_age(age_levels_s3, domain_levels, "<")
hypothesis_results <- hypothesis(m3r2, hyp_m3r2)
print(hypothesis_results$hypothesis)
write.csv(hypothesis_results$hypothesis, "saves/study3/s3r2-hypothesis-contrast-domain.csv", row.names = FALSE)

hypothesis(m_3, "r1_scale + age_factor5:r1_scale = 0")
hypothesis(m_3, "r1_scale + age_factor8:r1_scale = 0")
hypothesis(m_3, "r1_scale + age_factor11:r1_scale = 0")
hypothesis(m_3, "r1_scale + age_factor14:r1_scale = 0")
hypothesis(m_3, "r1_scale + age_factor17:r1_scale = 0")
hypothesis(m_3, "r1_scale + age_factor40:r1_scale = 0")
```
## variation
```{r}
m_3$data %>%
  group_by(age_factor, domain) %>%
  summarise(std = sd(r1_scale))

m_3$data %>%
  group_by(age_factor, domain) %>%
  summarise(std = sd(r2))
```
## Raw data
```{r}
ggplot(df, aes(x = r1_scale, y = r2, color = age_factor)) +
  geom_point(alpha = 0.3,size=1) +  # Add raw data points with some transparency
  geom_smooth(method = "lm", se = FALSE) +  # Overlay linear fits
  facet_wrap(~ age_factor, scales = "free_y") +  # One plot per age group
  labs(
    title = "Raw Relationship Between r1_scale and r2",
    x = "r1_scale",
    y = "r2",
    color = "Age Factor"
  ) +
  theme_minimal()
```

# Model diagnostics
```{r}

m1_residual <- m_1$data %>%
  add_residual_draws(m_1, ndraws=10) 

m1_residual %>%
  median_qi() %>%
  ggplot(aes(sample = .residual)) +
  geom_qq() +
  geom_qq_line() +
  ylab("theoretical") + xlab("samples")

ggsave("figures/diagnostic-m1.pdf", width = 8, height = 4)

pp_check(m_1)

m2_residual <- m_2$data %>%
  add_residual_draws(m_2, ndraws=10) 

m2_residual %>%
  median_qi() %>%
  ggplot(aes(sample = .residual)) +
  geom_qq() +
  geom_qq_line() +
  ylab("theoretical") + xlab("samples")
ggsave("figures/diagnostic-m2.pdf", width = 8, height = 4)

m3_residual <- m_3$data %>%
  add_residual_draws(m_3, ndraws=10) 
m_3$data %>%
  filter(age_factor==2) %>%
  ggplot(aes(x = r1_scale_r, y= r2)) +
  geom_point(alpha=0.2) + 
  ylab("r2") + xlab("r1")

m3_residual %>%
  ggplot(aes(sample = .residual)) +
  geom_qq() +
  geom_qq_line() +
  ylab("theoretical") + xlab("samples")

ggsave("figures/diagnostic-m3.pdf", width = 8, height = 4)
```

# Demographics
```{r}
demographic <- read_csv("results/s1-demographic.csv")
demographic <- read_csv("results/s2-demographic.csv")
demographic <- read_csv("results/s3-demographic.csv")

demographic %>% 
  filter(Status=="APPROVED", Age != "CONSENT_REVOKED") %>%
  mutate(Age = as.numeric(Age)) %>%
  summarize(mean_age = mean(Age),
            median_age = median(Age),
            max_age = max(Age),
            min_age = min(Age))
demographic %>% 
  filter(Status=="APPROVED", Age != "CONSENT_REVOKED") %>%
  count(`Ethnicity simplified`)
```

